\chapter{Muscles}\label{ch:Beef}
\section{control systems}
\subsection{Using EMG}

\section{BioMecanics}
The human autonomy is incredibly advanced. It is able to easily complete intricate tasks without much thought. 
Take the human Arm. It has 7 DOF and through them is able to pick and place most objects without damaging them, while orienting them any way desired. \cite{Redundan25:online}\\ 
The limbs can be described simply by addressing it as joints connected by rigid links, moved by the contractions of muscles. these contractions are made by running a current through them. The brain calculates what motions is needed for a given task, and then precisely activates relevant muscles. this allows for precise movements. \\
This is very similar to a Robotic manipulator with a similar amount of DOF.
Whenever the human arm make a movement, it does so through the use of muscles. And whenever a muscles is activated(contracting)  a change in currents can be measured, this is done with the use of an EMG (Electromyography). \cite{Electrom76:online}

\subsection{Electromyography}
Electromyography is a study of muscles electric activity \cite{Nerveled75:online}.
this is done by placing conductive pads or needles on or into the muscle in question. then whenever the mucle contracts it will register as an electrical signal
\subsection{muscles around shoulder}
basically: Pectoralis major(breast muscle) and Trapezius (either upper(neck) or middle (on top of shoulder, and upper back)) -- \discuss{ needs pic... but cant find a good one that's not copyright...:'( }